Dynamic Knapsack Problem

### 2021-06-26 v2-Manuscript/Manuscript.tex
working on a new version with streamlined model

\subsection{Questions}
\begin{itemize}
	\item Priority need to be added
\end{itemize}

@@

	\item It is assumed that there is no difference between how long a patient waits for their appointment within some limit ($TL$). 
	\begin{itemize}
		\item Let's assume our limit is 10 periods, there is no difference in terms of cost between patients who has been waiting for 1 period and patients waiting 10 period for their appointment (assuming they are the same category).  
		\item However, if a patient waits for 11 period for their appointment there should be some kind of penalty for the wait
		\item The penalty comes from increasing patient complexity. Higher complexities require more resources and are thus more costly overall in the system
	\end{itemize}

@@

	\item We assume that only specific reschedules are allowed (to simplify the model, and remove  redundancies)
	\begin{itemize}
		\item Good reschedules are allowed from any period after 2 into period 1
		\item Bad reschedules are only allowed from period 1 to period 2
	\end{itemize}

@@

\subsection{State Space}
\subsubsection{Description}
State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
    \item $\vec{ue} = ue_{tp}$ - Expected unist for  period $t$, and resource $p$
    \item $\vec{uu} = uu_{tp}$ - Used units for period $t$, and resource $p$
    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
\end{itemize}

@@

\subsubsection{Auxiliary Variables}
\begin{itemize}
	\item $\hat{uu}_{tp}$ - post-decision units used
	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
\end{itemize}
\subsubsection{Auxiliary Variable Definition}
\label{auxiliary constraints}
\begin{alignat}{10}
	& \hat{uu}_{tp} 
		&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
		&& \forall tp \\ 
	& \hat{pw}_{mdc} 
		&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
		&& \forall mdc \\ 
	& \hat{ps}_{tmdc} 
		&& = ps_{tmdc} + sc_{tmdc} + 
			\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
		&& \forall tmdc
\end{alignat}

@@

	\item Consistency Constraint
	\begin{equation}
		uu_{tp} = \sum_{mdc} U_{pdc} ps_{tmdc} \quad \forall tp
	\end{equation}
	\item Resource Usage Constraint
	\begin{equation}
		\hat{uu}_{tp} \le ue_{tp}+uv_{tp} \quad \forall tp
	\end{equation}

	\item Custom bounds on when reschedules are allowed
	\begin{alignat}{10}
		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t' 
	\end{alignat}

@@

	\item Bounds on states
	\begin{alignat}{10}
		& ue_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
		& uu_{tp} 	&& \le uen_{p} + max(ued_p) \quad 	&& \forall tp \\
		& pw_{mdc} 	&& \le pea_{dc} * 4 \quad 			&& \forall mdc \\
		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
	\end{alignat}
\end{itemize}

@@

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Expected Resources
	\begin{alignat}{10}
		& ue'_{1p} 
			&& 	= \overbrace{ ue_{2p} + ued_{p} }^\text{deviation}
				+ \overbrace{ ue_{1p} - \hat{uu}_{1p} }^\text{unused} + uv_{1p} \quad
			&& \forall p \in \{ \text{Carry Over Resources} \} \\
		& ue'_{1p} 
			&& 	= ue_{2p} + ued_{p} \quad
			&& \forall p \in \{ \text{Non Carry Over Resources} \} \\
		& ue'_{tp} 
			&& = ue_{t+1,p} \quad 
			&& \forall t \in \{2...T-1\} p \\
		& ue'_{Tp} 
			&& = uen_{p} \quad
			&& \forall p
	\end{alignat}

	\item Transition from $\vec{uu}$ to $\vec{uu'}$ - Used Resources	
	\begin{alignat}{10}
		& uu'_{tp}
			&& = \hat{uu}_{t+1,p} + 
				\overbrace{ \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc}) }^\text{
					change in complexities} \quad
			&& \forall t \in \{1...T-1\} \\
		& uu'_{Tp}
			&& = 0 \quad
			&& \forall p
	\end{alignat}

@@

\subsection{Costs}
Cost will come from 3 sources:  
\begin{itemize} 
	\item waiting ($cw$)
	\item rescheduling ($cc = \lceil cw^M \rceil$)
	\item resource violation ($M$)
\end{itemize}

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
				prevent infinite reschedules} + \\
	&	&&	+
				\overbrace{
					\sum_{tmdc} cw^{m} * t * (1/M)  (sc_{tmdc})
				}^\text{Prefer earlier appointments} \\ 
	&	&&  +
			\overbrace{
				(1.5cc+cw^{m}) \sum_{
				\substack{tt`mdc \\ t' > t}} 
				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
			\overbrace{ 
				(0.5cc) \sum_{
				\substack{tt`mdc \\ t' < t}}
				rsc_{tt'mdc}}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

@@

\section{Aproximate Dynamic Programming Model}
\subsection{Full ADP Model}
Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
\begin{equation}\begin{alignedat}{10}
	& v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{ps}) 
		&& =  \beta^0 + \sum_{tp} \beta_{tp}^{ue} ue_{tp} +
			\sum_{tp} \beta_{tp}^{uu} uu_{tp} + \\
		& && + \sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
\end{alignedat} \end{equation}

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 + \\
	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \bigg)+
		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{p} \bigg) + \\
	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
			( \hat{uu}_{t+1,p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})) \bigg) +
		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ue}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

@@

\begin{equation}
	\beta^{0}: \qquad (1-\gamma) \beta^{0}
\end{equation}
\begin{equation}
\beta^{ue}_{tp}: \qquad 
	\sum_{p} \beta_{1p}^{ue} \Big( ue_{1p} - \gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{tp}) \Big) + \sum_{t=2p}^{T} \beta_{tp}^{ue} \Big( ue_{tp} - \gamma (uen_{p}) \Big)
\end{equation}
\begin{equation}
\beta^{uu}_{tp}: \qquad \sum_{tp}^{T-1} \beta_{tp}^{uu} 
	\Big(uu_{tp} - \gamma 
	(\hat{uu}_{t+1p} + \sum_{mdc} E[pst_{t+1mdc}] (U_{pd+1c} - U_{pdc})) \Big) +
	\sum_{p} \beta_{Tp}^{uu} \Big( uu_{Tp} \Big)
\end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{pw}_{mdc}: \qquad 
	&& \sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) + 
	\sum_{m=1dc}^{M-1} \beta_{mdc}^{pw} 
	\Big( pw_{mdc} - \gamma 
		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
&	&& \sum_{dc} \beta_{Mdc}^{pw} 
	\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
\end{alignedat} \end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{ps}_{tmdc}: \qquad 
	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
	\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + \\
&	&& 
	\sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
	\Big( ps_{tmdc} - \gamma 
		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
\end{alignedat} \end{equation}

Let's say $E[V]$ is the addition of all parts above. Then the ADP model converted to expectation would look as follows:
\begin{equation}
	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ue} E[ue] + \sum \beta^{uu} E[uu]
		+ \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
\end{equation}
Subject to:
\begin{equation}
	E[V] \le c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) \quad \forall \vec{S} \vec{A} 
\end{equation}

@@

\begin{alignat}{10}
	& \beta^{0}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
	& \beta^{ue}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{1p} - 
			\gamma (uen_{p} + ue_{1p} - \hat{uu}_{1p} + uv_{1p}) \Big) \ge E[ue_{tp}]
		&&	\forall p \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ue_{tp} - 
			\gamma (uen_{p}) \Big) \ge E[ue_{tp}] 
		&& 	\forall t \in (2...T) p \\ 
	& \beta^{uu}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(uu_{tp} - 
		\gamma (\hat{uu}_{t+1p} + \sum_{mdc} E[pst_{t+1mdc}] (U_{pd+1c} - U_{pdc}) ) \Big) 
		\ge E[uu_{tp}]
		&&	\forall t \in \{1...T-1\}p \\
	&	&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(uu_{Tp} \Big) \ge E[uu_{Tp}]
		&&	\forall p \\
	&	\beta^{pw}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
		&&	\forall dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
		&&	\forall m \in \{1...M-1\} dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
		&&	\forall dc \\ 
	&	\beta^{ps}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
		&&	\forall tdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
		&&	\forall mdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
		&&	\forall \{1...T-1\} \{1...M-1\}dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
		&&	\forall \{1...T-1\} dc
\end{alignat}

>>>>

\subsection{Questions}
\begin{itemize}
	\item Should $ul$ definition include units violated?? it seems a constraint might be violated otherwise
\end{itemize}

@@

	\item It is assumed that patients do not change complexities within some limit ($TL$). 
	\begin{itemize}
		\item Let's assume our limit is 10 periods, patients will never change complexities within the 10 periods.  
		\item However, if a patient waits for 11 periods there is a possibility they increase complexity
	\end{itemize}

@@

	\item We assume that only specific reschedules are allowed (to simplify the model, and remove  redundancies)
	\begin{itemize}
		\item Good reschedules are allowed from any period after 2 into period 1
		\item Bad reschedules are only allowed from period 1 to any period after 2
	\end{itemize}

@@

\subsection{State Space}
\subsubsection{Description}
State is defined by current available and used resources, patient waitlist/demand, and patients already scheduled
\[  \vec{S}  = (\vec{ul}, \vec{pw}, \vec{ps}) \]
\begin{itemize}
	\item $\vec{ul} = ul_{p}$ - Units left over from previous period for resource $p$ plus deviation for that unit for period 1
    \item $\vec{pw} = pw_{mdc}$ - Patients of complexity $d$, CPU $c$, on a wait list for $m$ periods ($m$ of 0 - just arrived)
    \item $\vec{ps} = ps_{tmdc}$ - Patients of complexity $d$, CPU $c$, scheduled to period $t$, waiting for $m$ periods ($m$ of 0 - just arrived)
\end{itemize}

@@

\subsubsection{Auxiliary Variables}
\begin{itemize}
	\item $uvb_{tp}$ - binary variable to enforce $uv$ variable without objective function
	\item $\hat{ul}_{p}$ - post-decision unit leftover at period 1
	\item $ulb_{p}$ - binary variable to enforce $ul$ variable without objective function
	\item $\hat{uu}_{tp}$ - post-decision units used
	\item $\hat{pw}_{mdc}$ - post-decision patients waiting
	\item $\hat{ps}_{tmdc}$ - post-decision patients scheduled
\end{itemize}
\subsubsection{Auxiliary Variable Definition}
\label{auxiliary constraints}
\begin{alignat}{10}
	& \hat{uu}_{tp} 
		&& =  \sum_{mdc} U_{pdc} \hat{ps}_{tmdc} \quad
		&& \forall tp \\ 
	& \hat{pw}_{mdc} 
		&& = pw_{mdc} - \sum_{t} sc_{tmdc} \quad 
		&& \forall mdc \\ 
	& \hat{ps}_{tmdc} 
		&& = ps_{tmdc} + sc_{tmdc} + 
			\sum_{t} rsc_{tt'mdc} - \sum_{t'} rsc_{tt'mdc} \quad 
		&& \forall tmdc
\end{alignat}

\begin{itemize}

	\item Define Resource Violation Variable
	\begin{alignat}{10}
			& \hat{uv}_{tp} 
				&& \le  M(uvb_{tp}) \quad
				&& \forall tp \\
			& \hat{uv}_{1p} 
				&& \le  (\hat{uu}_{1p} - uen_{1p} - ul_{p}) + M(1-uvb_{tp}) \quad
				&& \forall p \\
			& \hat{uv}_{tp} 
				&& \le  (\hat{uu}_{tp} - uen_{tp}) + M(1-uvb_{tp}) \quad
				&& \forall t \in \{ 2..T \} p \\
	\end{alignat}

	\item Define Units Left Over Variable
	\begin{alignat}{10}
			& \hat{ul}_{p} 
				&& \ge 0 \quad 
				&& \forall p \\
			& \hat{ul}_{p} 
				&& \ge uen_{1p} + ul_{p} - \hat{uu}_{1p} \quad 
				&& \forall p \\
			& \hat{ul}_{p} 
				&& \le M (ulb_{p}) \quad 
				&& \forall p \\
			& \hat{ul}_{p} 
				&& \le (uen_{1p} + ul_{p} - \hat{uu}_{1p}) + M(1-ulb_{p}) \quad 
				&& \forall p
	\end{alignat}
\end{itemize}

@@

	\item Resource Usage Constraint
	\begin{alignat}{10}
			& \hat{uu}_{1p} 
			&& \le uen_{1p} + ul_{p} + uv_{1p} \quad 
			&& \forall p \\
		& \hat{uu}_{tp} 
			&& \le uen_{tp} + uv_{tp} \quad
			&& \forall t \in \{ 2..T \}p 
	\end{alignat}

	\item Custom bounds on when reschedules are allowed
	\begin{alignat}{10}
		& rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 2...T \}, t' \in \{2...T\} mdc \\
		% & rsc_{tt'mdc} && = 0 \quad && \forall t \in \{ 1 \}, t'\in \{ 3...T \} mdc  \\
		& rsc_{tt'mdc} && = 0 \quad && \forall tt'mdc, \text{where } t=t'=1 
	\end{alignat}

@@

	\item Bounds on states
	\begin{alignat}{10}
		& ul_{p} 	&& \le uen_{p} * 3 \quad 	&& \forall p \\
		& pw_{mdc} 	&& \le pea_{dc} * 20 \quad 			&& \forall mdc \\
		& ps_{tmdc} && \le pea_{dc} * 4 \quad 			&& \forall tmdc
	\end{alignat}
\end{itemize}

@@

\begin{enumerate}
	\item Transition from $\vec{ue}$ to $\vec{ue'}$ - Resource Carry Over
	\begin{alignat}{10}
		& ul'_{p} 
			&& = \hat{ul}_{p} + ued_{p} \quad 
			&& \forall p
	\end{alignat}

@@

\subsection{Costs}
Cost will come from 4 sources:  
\begin{itemize} 
	\item waiting ($cw$)
	\item rescheduling ($cc$)
	\item scheduling ($cs$)
	\item resource violation ($M$)
\end{itemize}

\begin{equation}\begin{alignedat}{10}
	& C = c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) = 
		&& 
			\overbrace{ \sum_{mdc} cw^{m} (\hat{pw}_{mdc}) }^\text{
				cost of waiting}  + 
			\overbrace{ \sum_{tmdc} cw^{M} (\hat{ps}_{tMdc})}^\text{
				prevent infinite reschedules} + \\
	&	&&	+
				\overbrace{
					\sum_{tmdc} cs^{t} (sc_{tmdc})
				}^\text{Prefer earlier appointments} \\ 
	&	&&  +
			\overbrace{
				(1.5cc) \sum_{
				\substack{tt`mdc \\ t' > t}} 
				rsc_{tt'mdc}}^\text{Bad Reschedule} - 
			\overbrace{ 
				(0.5cc) \sum_{
				\substack{tt`mdc \\ t' < t}}
				rsc_{tt'mdc}}^\text{Good Reschedule} + 
			M \sum_{tp} uv_{tp}
\end{alignedat}\end{equation}

@@

\section{Aproximate Dynamic Programming Model}
\subsection{Full ADP Model}
Let's convert it into ADP. We do that by changing $v(\vec{S})$ to an approximation as follows:
\begin{equation}\begin{alignedat}{10}
	& v(\vec{ul}, \vec{pw}, \vec{ps}) 
		&& =  \beta^0 + \sum_{p} \beta_{p}^{ul} ul_{p} +
			\sum_{mdc} \beta_{mdc}^{pw} pw_{mdc}  + 
			\sum_{tmdc} \beta_{tmdc}^{ps} ps_{tmdc}
\end{alignedat} \end{equation}

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ul}, \vec{pw}, \vec{ps}) v(\vec{ul}, \vec{pw}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 +
		\bigg( \beta^{ul}_{p} (\hat{ul}_{p} + uen_{d}) \bigg) + \\  
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ul}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

@@

\begin{equation}
	\beta^{0}: \qquad (1-\gamma) \beta^{0}
\end{equation}
\begin{equation}
\beta^{ul}_{p}: \qquad 
	\sum_{p} \beta_{p}^{ul} \Big( ul_{p} - \gamma ( \hat{ul}_{p}) \Big)
\end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{pw}_{mdc}: \qquad 
	&& \sum_{dc} \beta_{0dc}^{pw} \Big( pw_{0dc} - \gamma (pea_{dc}) \Big) + 
	\sum_{m=1dc}^{M-1} \beta_{mdc}^{pw} 
	\Big( pw_{mdc} - \gamma 
		(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) + \\
&	&& \sum_{dc} \beta_{Mdc}^{pw} 
	\Big( pw_{Mdc} - \gamma \sum_{M-1}^{M}
		(\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big)
\end{alignedat} \end{equation}
\begin{equation}\begin{alignedat}{10}
& \beta^{ps}_{tmdc}: \qquad 
	&& \sum_{tdc} \beta_{t0dc}^{ps} \Big( ps_{t0dc}) \Big) + 
	\sum_{mdc} \beta_{Tmdc}^{ps} \Big( ps_{Tmdc}) \Big) + \\
&	&& 
	\sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
	\Big( ps_{tmdc} - \gamma 
		(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \Big) + \\
&	&& \sum_{t=1dc}^{T-1} \beta_{tMdc}^{ps} 
	\Big( ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}]) \Big)
\end{alignedat} \end{equation}

Let's say $E[V]$ is the addition of all parts above. Then the ADP model converted to expectation would look as follows:
\begin{equation}
	\max_{\vec{\beta}} \Big( \sum \beta^{0} + \sum \beta^{ut} E[ut] + \sum \beta^{pw} E[pw] + \sum \beta^{ps} E[ps] \Big)
\end{equation}
Subject to:
\begin{equation}
	E[V] \le c(\vec{pw}, \vec{sc}, \vec{rsc}, \vec{uv}) \quad \forall \vec{S} \vec{A} 
\end{equation}

@@

\begin{alignat}{10}
	& \beta^{0}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} (1 - \gamma) = 1 \\
	& \beta^{ul}: 
		&& 	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ul_{p} - 
			\gamma (\hat{ul}_{p}) \Big) \ge E[ul_{p}]
		&&	\forall p \\
	&	\beta^{pw}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{0dc} - 
		\gamma (pea_{dc}) \Big) \ge E[ps_{0dc}]
		&&	\forall dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{mdc} - 
		\gamma (\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \Big) \ge E[pw_{mdc}]
		&&	\forall m \in \{1...M-1\} dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(pw_{Mdc} - \gamma 
			\sum_{M-1}^{M} (\hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}]) \Big) \ge E[pw_{Mdc}]
		&&	\forall dc \\ 
	&	\beta^{ps}: 
		&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{t0dc} \Big) \ge E[ps_{t0dc}]
		&&	\forall tdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{Tmdc} \Big) \ge E[ps_{Tmdc}]
		&&	\forall mdc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tmdc} - \gamma 
			(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tmdc}] \;
		&&	\forall \{1...T-1\} \{1...M-1\}dc \\
	&	&&	\sum_{\vec{S}\vec{A}}\vec{w} \Big(ps_{tMdc} - \gamma \sum_{M-1}^{M}
		(\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{d}]) \Big) \ge E[ps_{tMdc}] \;
		&&	\forall \{1...T-1\} dc
\end{alignat}
